### 2019-03-06 Thesis_Latex/Thesis/Acknowledgements/Acknowledgements.tex
update thesis

\chapter*{Acknowledgements}
\thispagestyle{empty}
Eventuali ringraziamenti personali.

>>>>

\chapter*{Ringraziamenti/Acknowledgements}
\thispagestyle{empty}
dedica a parenti e amici

The research work for this thesis was carried out at the Laboratory for Automation and Robotics (LAR) in the Department of Mechanical Engineering of Aveiro (Portugal), during a period of 5 months as an exchange student.
\begin{figure}[!h]
	\centering
	\includegraphics[width=0.50\textwidth]{../figure/logo_ua.png}
	\label{fig:logo_ua}
\end{figure}

I would like to express my gratitude to Professor Vitor Santos, for welcoming me at the Laboratory for Automation and Robotics and making possible my experience of study at the University of Aveiro. His help has been invaluable both personally and academically. Moreover I would like to thank Professor Angelo Cenedese for his advices and his help during this work.

### 2019-03-06 Thesis_Latex/Thesis/Chapter4/Chapter4.tex
update thesis

\chapter{Moving Obstacle Avoidance}
\section{Problem Formulation}
\section{Design of Adaptive MPC}
\section{Simulation Results}

>>>>

\chapter{Moving Obstacle Avoidance}

\section{Problem Formulation}
% COLLISION AVOIDANCE FIGURE
\begin{figure}[!h]
	\centering
	\includegraphics[width=\textwidth]{../figure/obstacleAvoidance/obstacleAvoidance.pdf}
	\caption{Problem description of collision avoidance on a road with only two lanes.}
	\label{fig:obstacleAvoidance}
\end{figure}
% BICYCLE MODEL
\begin{figure}[!h]
	\centering
	\includegraphics[width=0.80\textwidth]{../figure/car_model.pdf}
	\caption{Bicycle model of a car, (adapted from \cite{siciliano}).}
	\label{fig:car_model}
\end{figure}
\section{Design of Adaptive MPC}
% FLOWCHART
\begin{figure}[!h]
	\centering
	\includegraphics[width=\textwidth]{../figure/flowchart/flowchart.pdf}
	\caption{Behaviour planning conditional flowchart.}
	\label{fig:flowchart}
\end{figure}
% FIGURE CONSTRAINT
\begin{figure}[!h]
	\centering
	\includegraphics[width=\textwidth]{../figure/constraint/constraint.pdf}
	\caption{Constraints in the case of left overtaking.}
	\label{fig:constraint}
\end{figure}

\section{Simulation Results}
% ONE MOVING OBSTACLE
\begin{figure}[h!]
	\centering
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/one_obstacle_right_overtaking/overtaking_start.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/one_obstacle_right_overtaking/overtaking_middle.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/one_obstacle_right_overtaking/overtaking_middle_end.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/one_obstacle_right_overtaking/overtaking_end.pdf}
	\end{minipage}
	\caption{Simulation of right overtaking with one moving obstacle that moves in the same direction as the vehicle.}
	\label{fig:obstacleAvoidance_one_obstacle}
\end{figure}
% ALGORITHM FOR RIGHT OVERTAKING OF ONE MOVING OBSTACLE
\begin{algorithm}%[b]
	\caption{Right Overtaking if an obstacle is detected}
	\small
	\begin{algorithmic}[1]
		\Function{RightOvertaking}{car, obstacle, road}
		\State $x_\text{min} \gets \text{car}X $,  $x_\text{max} \gets +\infty$;
		\State obsYrr = obstacle.RearRightSafeY;
		\State obsXrr = obstacle.RearRightSafeX;
		\If{ATLASCAR2 is behind the obstacle} 
		\If{ATLASCAR2 is in the adjacent lane}
		\State $cS \gets 0$; $cI \gets \text{obsYrr}$;
		\Else
		\State $cS \gets \text{tan}(\text{atan2}(\frac{\text{obsYrr}-\text{ carY}}{\text{obsXrr}-\text{carX}},1))$;
		\State $cI \gets \text{obsYrr}-cS*\text{obsXrr}$;
		\EndIf
		\Else
		\If{ATLASCAR2 is parallel to the obstacle}
		\State $cS \gets 0$; $cI \gets \text{obsYrr}$;
		\Else
		\State $cS \gets 0$; $cI \gets W/2$;
		\EndIf
		\EndIf
		\State \Return $x_\text{min}$, $x_\text{max}$, $cI$, $cS$
		\EndFunction
	\end{algorithmic}
	\label{alg:rightOvertaking}
\end{algorithm}
% OVERALL SCHEME ONE MOVING OBSTACLE
\begin{figure}[!h]
	\centering
	\includegraphics[width=\textwidth]{../figure/MovingObstacleAvoidance.pdf}
	\caption{Overall procedure scheme moving obstacle avoidance.}
	\label{fig:MovingObstacleAvoidance}
\end{figure}
% MULTIPLE MOVING OBSTACLE
\begin{figure}[!h]
	\centering
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/random_N_obstacles/overtaking_random_2.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/random_N_obstacles/overtaking_random.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/random_N_obstacles/overtaking_random_1.pdf}
	\end{minipage}
	\caption{Simulations of overtaking with $N = 2,3,4$ moving obstacles that drive in the opposite direction with respect to the ATLASCAR2.}
	\label{fig:obstacleAvoidance_random}
\end{figure}

% BRAKING THREE OBSTACLE
\begin{figure}[!h]
	\centering
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/braking_0.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/braking_1.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/braking_2.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/braking_3.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/braking_4.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/braking_5.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/braking_6.pdf}
	\end{minipage}
	\caption{Simulation of braking and overtaking obstacles.}
	\label{fig:braking}
\end{figure}
% RESULTS BRAKING THREE OBSTACLES
\begin{figure}[!t] %vs changes to t instead of b
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/VelocityVsTime.pdf}
		\vspace{-17pt}
		\subcaption{}\label{fig:velocity_braking}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/ThrottleVsTime.pdf}
		\vspace{-17pt}
		\subcaption{}\label{fig:throttle_braking}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/SteeringAngleVsTime.pdf}
		\vspace{-17pt}
		\subcaption{}\label{fig:delta_braking}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/HeadingAngleVsTime.pdf}
		\vspace{-17pt}
		\subcaption{}\label{fig:theta_braking}
	\end{minipage}
	\caption{Time signals of the ATLASCAR2 in the simulation of braking and overtaking in the situation illustrated in Fig. \ref{fig:braking}.}
	\label{fig:components}
\end{figure}

### 2019-03-06 Thesis_Latex/Thesis/Chapter5/Chapter5.tex
update Matlab files
update thesis

\chapter{Moving Obstacle Avoidance}
\section{Problem Formulation}
\section{Design of Adaptive MPC}
\section{Simulation Results}

>>>>

\chapter{Lane Following}
\section{Problem Formulation}
\begin{figure}[!h]
	\centering
	\includegraphics[width=0.75\textwidth]{../figure/laneFollowing/laneFollowing.pdf}
	\caption{Problem description of a lane following system.}
	\label{fig:laneFollowing}
\end{figure}
\section{Design of Adaptive MPC}
\section{Simulation Results}
\begin{table}[!h]
	\centering
	\begin{tabular}{|c|c|}
		\hline
		Parameters          & Values      \\
		\hline
		$m$          & \SI{1575}{kg}              \\
		$I_z$         & \SI{2875}{kgm^2}               \\
		$l_F$           & \SI{1.2}{m}               \\
		$l_R$         & \SI{1.6}{m}               \\
		$C_F$          & \SI{19000}{\newton/rad}      \\
		$C_R$           & \SI{33000}{\newton/rad}  \\
		$\tau$             & 0.2                \\
		$V_0$           & \SI{15}{m/s}       \\
		$V_{\text{set}}$          & \SI{20}{m/s}   \\
		$T_s$         & \SI{0.02}{s}          \\
		\hline
	\end{tabular}
\end{table}

\begin{figure}[!t]
	\centering
	\begin{minipage}[t]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/Reference.pdf}
		\vspace{-17pt}
		\subcaption{}
		\label{fig:reference_laneFollowing}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/Curvature.pdf}
		\vspace{-17pt}
		\subcaption{}
		\label{fig:curvature_laneFollowing}
	\end{minipage}
	\caption{Desired path and curvature of the ATLASCAR2 in a simulation of \SI{20}{s}}
	\label{fig:laneFollowing_desired}
	\vspace{-30pt}
\end{figure}

\begin{figure}[!t]
	\centering
	\begin{minipage}[t]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/LongitudinalVelocityVsTime.pdf}
		\subcaption{Longitudinal velocity $V_x$ with respect to time.}
		\label{fig:longitudinal_velocity_laneFollowing}
	\end{minipage}
	\begin{minipage}[t]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/AccelerationVsTime.pdf}
		\subcaption{Acceleration $u_1$ with respect to time.}
		\label{fig:acceleration_laneFollowing}
	\end{minipage}
	\begin{minipage}[t]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/SteeringAngleVsTime.pdf}
		\subcaption{Steering angle $u_2$ with respect to time.}
		\label{fig:steering_laneFollowing}
	\end{minipage}
	%\begin{minipage}[t]{\columnwidth}
	%	\includegraphics[width=\columnwidth]{../../MATLAB/lane_following/figure/RelativeYawAngleVsTime.pdf}
	%	\subcaption{Relative yaw angle $e_2$ with respect to time.}
	%	\label{fig:relative_yaw_angle_laneFollowing}
	%\end{minipage}
	\begin{minipage}[t]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/LateralDeviationVsTime.pdf}
		\subcaption{Lateral deviation $e_1$ with respect to time.}
		\label{fig:lateral_deviation_laneFollowing}
	\end{minipage}
	\caption{Time signals of the ATLASCAR2 in the simulation with a sinusoidal path.}
	\label{fig:laneFollowing_signals}
\end{figure}

\begin{figure}[!h]
	\centering
	\includegraphics[width=1\textwidth]{../figure/lane_following_AMPC.pdf}
	\caption{Overall procedure scheme lane following.}
	\label{fig:scheme_lane_following}
\end{figure}

### 2019-03-06 Thesis_Latex/Thesis/Introduction/Introduction.tex
update thesis

\subsection{ATLASCAR}\label{sec:ATLASCAR}
\begin{figure}[!h]
	\centering
	\includegraphics[width=\textwidth]{../figure/atlascar1.jpg}
	\caption{The car used in ATLASCAR, based on Ford Escort Station Wagon of 1998 (adapted from \cite{Pereira2012}).}
	\label{fig:atlascar1}
\end{figure}

\subsection{ATLASCAR2}\label{sec:ATLASCAR2}
\begin{figure}[!h]
	\centering
	\includegraphics[width=\textwidth]{../figure/atlascar2.jpg}
	\caption{The vehicle used in ATLASCAR2, based on an electric car, a Mitsubishi iMiEV of 2015 (adapted from \cite{Ricardo:Thesis:2018}).}
	\label{fig:atlascar2}
\end{figure}
\section{Context of the Problem and Motivation}
\section{Proposed Approach}
\section{Thesis Outline and Contributions}

>>>>

\subsection{ATLASCAR}\label{sec:ATLASCAR}
Driven by the positive results achieved with scale models and years of navigation experience in controlled environments, in 2010 the Group of Automation and Robotics decided to invest in a large-scale project, ATLASCAR (Figure \ref{fig:atlascar1}). The vehicle used for this project was a Ford Escort Station Wagon of 1998 powered by a gasoline internal combustion engine, in which several sensors, processing units and actuators were installed. On-board sensors processed data collected from the vehicle and its surroundings, with different LIDARs for obstacle detection and environmental reconstruction, pedestrian detection cameras and a Global Navigation Satellite System (GNSS) for location and route planning. After passing through the processing units, these data were sent to the actuators that allowed the movement and execution of the maneuvers in a completely autonomous way on the part of the vehicle. To power all the equipment, a Uninterruptible Power Supply (UPS) was used, loaded from an auxiliary alternator. During this project, many works were developed in the Laboratory for Automation and Robotics, many of which produced master thesis. For example, in 2014 Cabral de Azevedo \cite{Azevedo2014} developed a module to detect pedestrians using sensory fusion of LIDAR and vision data while in 2016 Vieira da Silva \cite{Silva2016} created a multisensory calibration module that was exported to subsequent projects.
\begin{figure}[!h]
	\centering
	\includegraphics[width=\textwidth]{../figure/atlascar1.jpg}
	\caption{The car used in ATLASCAR, based on Ford Escort Station Wagon of 1998 (adapted from \cite{Pereira2012}).}
	\label{fig:atlascar1}
\end{figure}

\subsection{ATLASCAR2}\label{sec:ATLASCAR2}
Given the different limits, to continue the project, in 2016, a new vehicle was acquired: ATLASCAR2 (Figure \ref{fig:atlascar2}). This time it was chosen as a platform
an electric car, a Mitsubishi iMiEV, with an autonomy range of \SI{100}{km}. The fact that the vehicle is electric allows to use the energy stored in the batteries, making it easier to power the sensors installed. In fact, despite the short time of existence, 3 LIDARs, a camera, inclinometry sensors and a GNSS unit are already installed on the ATLASCAR2. Many of these sensors were transferred from ATLASCAR to this project during the work of Madureira Correia \cite{Madureira2017} in 2017, where a module for detecting free space around the car was also developed while in 2018 Ricardo Silva \cite{Ricardo:Thesis:2018} created a local navigation module for driver assistance in the immediate decision making, identifing a solution based on a multiple hypothesis approach.
\begin{figure}[!h]
	\centering
	\includegraphics[width=\textwidth]{../figure/atlascar2.jpg}
	\caption{The vehicle used in ATLASCAR2, based on an electric car, a Mitsubishi iMiEV of 2015 (adapted from \cite{Ricardo:Thesis:2018}).}
	\label{fig:atlascar2}
\end{figure}

\section{Autonomous Cars}
The modern automobile companies keep coming up with newer autonomous features in their recent models. Technological advancements seen every day in areas like information technology, communication, data analysis and storage etc. is not exclusive to these areas alone. The realm of autonomous cars is also progressing at a rapid rate these days \cite{Bimbraw2015}. Google's development of self-driving technology began in January 2009. The initial objective of the project was to develop a car able to navigate on highways with minimal human intervention. In December 2016, the unit was renamed Waymo; this name derived from its mission, "a new way forward in mobility". Waymo moved to further test its cars on public roads after becoming its own subsidiary.
\begin{figure}[!h]
	\centering
	\begin{minipage}[t]{0.65\textwidth}
		\includegraphics[width=\textwidth]{../figure/veiculos0.png}
		\subcaption{Google's Firefly self-driving prototype in 2015 (adapted from \cite{waymoh}).}
		\label{fig:veiculos0}
	\end{minipage}
	\begin{minipage}[t]{0.65\textwidth}
		\includegraphics[width=\textwidth]{../figure/veiculos1.png}
		\subcaption{Waymo Chrysler Pacifica Hybrid self-driving prototype in 2017 (adapted from \cite{waymoh}).}
		\label{fig:veiculos1}
	\end{minipage}
	\caption{Some of the Waymo/Google prototypes tested across multiple locations in the Unided States in recent years.}
	\label{fig:waymo}
\end{figure}

Waymo uses LIDAR which sends out millions of laser beams per second to build up a detailed picture of the world all 360 degrees around it. It also uses radar to detect how far away objects are and their speed and high-resolution cameras detect visual information like whether a traffic signal is red or green. It then combines all that data to understand the world around it and predict what those things might do next. It can do that for things up to three football fields away. Based on all this information, Waymo's software determines the exact trajectory, speed, lane and steering maneuvers needed to progress along this route safely \cite{waymoh} \cite{waymot}.
With the advances in autonomous technology, VIAC or VisLab Intercontinental Autonomous Challenge was one of the major competitions which led to improvements in the testing and analysis of autonomous vehicles and robotics. It was a 13,000 kilometers trip, nearly three months from Parma, Italy to Shanghai, China from July 20, 2010 to October 28, 2010. It involved four autonomous vehicles with negligible human intervention and high level of autonomy \cite{Broggi2010}.
\begin{figure}[!h]
	\centering
	\includegraphics[width=0.65\textwidth]{../figure/veiculos4.png}
	\caption{BRAiVE prototype developted by VisLab, based on a Hyundai Sonata (adapted from \cite{Broggi2013}).}
	\label{fig:veiculos4}
\end{figure}
\section{Context of the Problem and Motivation}
\section{Proposed Approach}
\section{Thesis Outline and Contributions}
